Reducing iptables configuration complexity using chains

### 2014-05-03 iptables/presentation.tex
add conlusions to overview
Add CC license to iptables presentation, close #1
display contact on bottom of page
use macro to display 2 dashes

\documentclass[14pt]{beamer}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage[T1]{fontenc}
\usetheme{Madrid}

@@

@@

@@

      \small{iptables -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport http -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\

@@

      \small{-A \textbf{INPUT} -m tcp -p tcp --dport ssh -j ACCEPT}

@@

      \small{-A INPUT \textbf{-m tcp -p tcp --dport ssh -s 10.0.0.0/8} -j ACCEPT}

@@

      \small{-A INPUT -m tcp -p tcp --dport ssh \textbf{-j ACCEPT}}

@@

      \small{-A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\

@@

      -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\

@@

      -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport https -j ACCEPT}

@@

      -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\
      {\color{blue}-A OUTPUT -m tcp -p tcp --sport ssh -j ACCEPT\\
      -A OUTPUT -m tcp -p tcp --sport 80 -j ACCEPT\\
      -A OUTPUT -m tcp -p tcp --sport https -j ACCEPT}}

@@

      -A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport https -j ACCEPT\\
      {\color{blue}-A OUTPUT -m state --state ESTABLISHED,RELATED -j ACCEPT}}

@@

      -A INPUT -m state --state ESTABLISHED,RELATED -j ACCEPT}

@@

      \small{-A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp --dport https -j ACCEPT}

@@

      \small{-A INPUT -p tcp -m tcp -s 10.100.2.3 --dport 22 -j ACCEPT\\
      -A INPUT -p tcp -m tcp -s 10.100.2.4 --dport 22 -j ACCEPT\\
      -A INPUT -p tcp -m tcp -s 10.100.2.7 --dport 22 -j ACCEPT\\
      -A INPUT -p tcp -m tcp -s 10.100.2.3 --dport 10000 -j ACCEPT\\
      -A INPUT -p tcp -m tcp -s 10.100.2.4 --dport 10000 -j ACCEPT\\
      -A INPUT -p tcp -m tcp -s 10.100.2.7 --dport 10000 -j ACCEPT}

@@

      \small{-A INPUT -p tcp -m tcp --dport 22 -j admin\_IP\\
      -A INPUT -p tcp -m tcp --dport 10000 -j admin\_IP}

@@

      \small{-A INPUT -p tcp -m tcp --dport 445 -j admin\_IP\\
      -A INPUT -p tcp -m tcp --dport 445 -j webmaster\_IP\\
      -A INPUT -p tcp -m tcp --dport 139 -j admin\_IP\\
      -A INPUT -p tcp -m tcp --dport 139 -j webmaster\_IP}

@@

      \small{\sout{{\color{red}-A INPUT -p tcp -m tcp --dport 445 -j admin\_IP}}\\
      -A INPUT -p tcp -m tcp --dport 445 -j webmaster\_IP\\
      \sout{{\color{red}-A INPUT -p tcp -m tcp --dport 139 -j admin\_IP}}\\
      -A INPUT -p tcp -m tcp --dport 139 -j webmaster\_IP}

@@

  \begin{frame}
    \frametitle{Conclusion}
    \begin{itemize}
      \item use ESTABLISHED state to reduce number of rules
      \item using chains makes your rules easier readable and maintainable
      \item chains can be reused for several rules
      \item chains can be chained together
      \item faster, because it only jumps to a chain when a rule matches
    \end{itemize}
  \end{frame}
  \begin{frame}
   \frametitle{Questions}
    Thanks for your attention!\\
    Questions?\\
    Contact
    \begin{itemize}
      \item Blog : \href{http://ruleant.blogspot.com/}{http://ruleant.blogspot.com}
      \item Twitter : \href{https://twitter.com/dcadriaenssens}{@dcadriaenssens}
    \end{itemize}
  \end{frame}
\end{document}

>>>>

\documentclass[14pt]{beamer}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage[T1]{fontenc}
\usetheme{Madrid}

% macro for double dash
\newcommand{\dd}{{\texttt{-{}-}}}

%% Enable license helpers
\graphicspath{{../cc_beamer/}}
\input{../cc_beamer/cc_beamer}

@@

  \vfill
    \begin{center}
      \CcGroupBySa{0.83}{0.95ex}\\[2.5ex]
        {\tiny\CcNote{\CcLongnameBySa}}
        \vspace*{-2.5ex}
    \end{center}

@@

      \item conclusions

@@

      \small{iptables -A INPUT -m tcp -p tcp \dd dport ssh -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp \dd dport http -j ACCEPT\\
      iptables -A INPUT -m tcp -p tcp \dd dport https -j ACCEPT\\

@@

      \small{-A \textbf{INPUT} -m tcp -p tcp \dd dport ssh -j ACCEPT}

@@

      \small{-A INPUT \textbf{-m tcp -p tcp \dd dport ssh -s 10.0.0.0/8} -j ACCEPT}

@@

      \small{-A INPUT -m tcp -p tcp \dd dport ssh \textbf{-j ACCEPT}}

@@

      \small{-A INPUT -m tcp -p tcp \dd dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp \dd dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp \dd dport https -j ACCEPT\\

@@

      -A INPUT -m tcp -p tcp \dd dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp \dd dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp \dd dport https -j ACCEPT\\

@@

      -A INPUT -m tcp -p tcp \dd dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp \dd dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp \dd dport https -j ACCEPT}

@@

      -A INPUT -m tcp -p tcp \dd dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp \dd dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp \dd dport https -j ACCEPT\\
      {\color{blue}-A OUTPUT -m tcp -p tcp \dd sport ssh -j ACCEPT\\
      -A OUTPUT -m tcp -p tcp \dd sport 80 -j ACCEPT\\
      -A OUTPUT -m tcp -p tcp \dd sport https -j ACCEPT}}

@@

      -A INPUT -m tcp -p tcp \dd dport ssh -j ACCEPT\\
      -A INPUT -m tcp -p tcp \dd dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp \dd dport https -j ACCEPT\\
      {\color{blue}-A OUTPUT -m state \dd state ESTABLISHED,RELATED -j ACCEPT}}

@@

      -A INPUT -m state \dd state ESTABLISHED,RELATED -j ACCEPT}

@@

      \small{-A INPUT -m tcp -p tcp \dd dport 80 -j ACCEPT\\
      -A INPUT -m tcp -p tcp \dd dport https -j ACCEPT}

@@

      \small{-A INPUT -p tcp -m tcp -s 10.100.2.3 \dd dport 22 -j ACCEPT\\
      -A INPUT -p tcp -m tcp -s 10.100.2.4 \dd dport 22 -j ACCEPT\\
      -A INPUT -p tcp -m tcp -s 10.100.2.7 \dd dport 22 -j ACCEPT\\
      -A INPUT -p tcp -m tcp -s 10.100.2.3 \dd dport 10000 -j ACCEPT\\
      -A INPUT -p tcp -m tcp -s 10.100.2.4 \dd dport 10000 -j ACCEPT\\
      -A INPUT -p tcp -m tcp -s 10.100.2.7 \dd dport 10000 -j ACCEPT}

@@

      \small{-A INPUT -p tcp -m tcp \dd dport 22 -j admin\_IP\\
      -A INPUT -p tcp -m tcp \dd dport 10000 -j admin\_IP}

@@

      \small{-A INPUT -p tcp -m tcp \dd dport 445 -j admin\_IP\\
      -A INPUT -p tcp -m tcp \dd dport 445 -j webmaster\_IP\\
      -A INPUT -p tcp -m tcp \dd dport 139 -j admin\_IP\\
      -A INPUT -p tcp -m tcp \dd dport 139 -j webmaster\_IP}

@@

      \small{\sout{{\color{red}-A INPUT -p tcp -m tcp \dd dport 445 -j admin\_IP}}\\
      -A INPUT -p tcp -m tcp \dd dport 445 -j webmaster\_IP\\
      \sout{{\color{red}-A INPUT -p tcp -m tcp \dd dport 139 -j admin\_IP}}\\
      -A INPUT -p tcp -m tcp \dd dport 139 -j webmaster\_IP}

@@

  \begin{frame}
    \frametitle{Conclusion}
    \begin{itemize}
      \item use ESTABLISHED state to reduce number of rules
      \item using chains makes your rules easier readable and maintainable
      \item chains can be reused for several rules
      \item chains can be chained together
      \item faster, because it only jumps to a chain when a rule matches
    \end{itemize}
  \end{frame}
  \begin{frame}
   \frametitle{Questions}
    Thanks for your attention!\\
    Questions?
    \vfill
    Contact
    \begin{itemize}
      \item Blog : \href{http://ruleant.blogspot.com/}{http://ruleant.blogspot.com}
      \item Twitter : \href{https://twitter.com/dcadriaenssens}{@dcadriaenssens}
    \end{itemize}
  \end{frame}
\end{document}
